Software Citation Principles

### 2016-03-31 sc-principles/software-citation-principles.tex
Added references to DOAP and schema.org

Notable examples of community efforts around metadata include the AAS workshop~\cite{aas-software-index}, Project CRediT~\cite{casrai-credit}, Ontosoft~\cite{ontosoft}, CodeMeta~\cite{codemeta}.

>>>>

Notable examples around metadata include DOAP~\cite{DOAP}, an early metadata term set used by the Open Source Community, as well as more recent community efforts like the AAS workshop~\cite{aas-software-index}, Project CRediT~\cite{casrai-credit}, Ontosoft~\cite{ontosoft}, CodeMeta~\cite{codemeta}, or the terms and classes defined at \url{schema.org} related to the \url{https://schema.org/SoftwareApplication} class.
